---
title: "Replication"
author: "Pawonee"
date: "10/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal is to replicate tables from an exisiting Urban paper. The paper I will use is titled:

# The Efficiency of Race-Neutral Alternatives to Race-Based Affirmative Action: Evidence from Chicago's Exam Schools
By: Glenn Ellison & Parag A. Pathak

Refer to attached link for AER : https://www.openicpsr.org/openicpsr/project/120529/version/V1/view?path=/openicpsr/120529/fcr:versions/V1&type=project

First, I installed some packages as per instruction:
install.packages(c("leaps","gelnet","doParallel","foreach","hdm"))
I will work on cleaning data from the Census Socioeconomic data here:

```{r}
library(stargazer)
library(plm)
library(foreign)
library(tidyverse)
tract_data <- read.csv("/Users/pawonee/Desktop/PhD/Sem3/Urban/School/public_use_data/raw/Summary of Census Socioeconomic Data 2012-2013.csv" ,header=TRUE, stringsAsFactors=FALSE) %>%
  mutate (income = Estimated.Median.Family.Income.Cumulative.Percentage,
         educ = Educational.Attainment.Score.Cumulative.Percentage,
         single = X..of.Single.Parent.Households,
         owner = X..of.Owner.Occupied.Homes.Cumulative.Percentage,
         english = X..of.Population.Speaking.a.Language.Other.than.English,
         isat = Weighted.Average.ISAT.Performance.at.Attendance.Area.Schools,
         tracta = TRACT,
         tracta = 100*tracta,
         factorsocioeconomictier = X6.Factor.Socioeconomic.Tier)

#for (income educ single owner english isat in tract_data) { mutate (tract = str(tracta))}
```

Creating a simpler data frame:
```{r}
tract_update <- data.frame(tract_data$TRACT,tract_data$tracta, tract_data$income, tract_data$single, tract_data$owner, tract_data$english, tract_data$isat, tract_data$factorsocioeconomictier)

#Checking impact of household being single parent on educational attainment score:
m1 <-lm(educ~single, data = tract_data)
#doesnt work because percentage sign
attach(tract_data)
plot(educ, single)
abline(lm(educ~single))
title("Regression of % of single parent households on education attainment score")
```





The analysis table is done using:
```{r}
regList <- c("lasso", "stepwise", "gelnet lasso", "lasso with hdm", "lasso glmnet min")
for (regType in regList)  {
  print(paste("Now running '", regType, ".R'", sep = ""))
  source(paste(code, "/", regType, ".R", sep = ""))
}
```{r}
